Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-20 lqg-strings.tex
Used conformal symmetry to simplify eq(40) and eq(39), reducing to eq(22)

Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the induced metrics:
\begin{equation} \label{eqn:variation-wrt-g}
	\frac{\delta S_{P B}}{\delta g^{c d}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{multline} \label{eqn:g-em-tensor}
	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
\end{multline}
\begin{equation*}
	\Downarrow
\end{equation*}
\begin{equation} \label{eqn:g-expression}
	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation} \label{eqn:g's-f-function}
	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu},
\end{equation}
and completely analogously for the $H_{\mu \nu}$ metric,
\begin{equation} \label{variation-wrt-h}
	\frac{\delta S_{P B}}{\delta h^{c d}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{multline} \label{h-em-tensor}
	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
\end{multline}
\begin{equation*}
	\Downarrow
\end{equation*}
\begin{equation} \label{h-expression}
	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
\end{equation}
with
\begin{equation} \label{h's-f-function}
	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}

As for the embbeding fields equation, we get a wave equation for the combined metric
\begin{equation} \label{eqn:variation-wrt-X}
	\frac{\delta S_{P B}}{\delta X^{\lambda}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:bimetric-wave-equation}
	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} F_{\mu \lambda} = \frac{1}{2} f^{\prime a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \frac{\partial F_{\mu \nu}}{\partial X^{\lambda}} ,
\end{equation}
where
\begin{equation} \label{eqn:coupled-ws-metric}
	f^{\prime a b} & = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
\end{equation}
\begin{equation} \label{eqn:combined-bulk-metric}
	F_{\mu \nu}    & = G_{\mu \nu} + H_{\mu \nu} ,
\end{equation}
in which we add a prime in the coupled metric $f^{\prime a b}$ since it is not quite the metric induced by the combined bulk metric $F_{\mu \nu}$.

>>>>

Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the induced metrics:
\begin{equation} \label{eqn:variation-wrt-g}
	\frac{\delta S_{P B}}{\delta g^{c d}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{multline} \label{eqn:g-em-tensor}
	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
\end{multline}
\begin{equation*}
	\Downarrow
\end{equation*}
\begin{equation} \label{eqn:g-expression}
	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation} \label{eqn:g's-f-function}
	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu},
\end{equation}
and completely analogously for the $H_{\mu \nu}$ metric,
\begin{equation} \label{eqn:variation-wrt-h}
	\frac{\delta S_{P B}}{\delta h^{c d}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{multline} \label{eqn:h-em-tensor}
	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
\end{multline}
\begin{equation*}
	\Downarrow
\end{equation*}
\begin{equation} \label{eqn:h-expression}
	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
\end{equation}
with
\begin{equation} \label{eqn:h's-f-function}
	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}

As for the embbeding fields equation, we get a wave equation for the coupled metric
\begin{equation} \label{eqn:variation-wrt-X}
	\frac{\delta S_{P B}}{\delta X^{\lambda}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:bimetric-wave-equation}
	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} F_{\mu \lambda} = \frac{1}{2} f^{\prime a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \frac{\partial F_{\mu \nu}}{\partial X^{\lambda}} ,
\end{equation}
where
\begin{equation} \label{eqn:coupled-ws-metric}
	f^{\prime a b} & = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
\end{equation}
\begin{equation} \label{eqn:combined-bulk-metric}
	F_{\mu \nu}    & = G_{\mu \nu} + H_{\mu \nu} ,
\end{equation}
in which we add a prime in the coupled metric $f^{\prime a b}$ since it is not quite the metric induced by the combined bulk metric $F_{\mu \nu}$. Since 2D metrics can always be written as a conformal metric, it is easy to see that eq(\ref{eqn:coupled-ws-metric}) can be recast as
\begin{equation} \label{eqn:conformal-coupled-metric}
	f^{\prime a b} = T \eta ^{a b} + T' \eta ^{a b} = (T + T') \eta ^{a b} ,
\end{equation}
and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$, we see that eq(\ref{eqn:bimetric-wave-equation}) trivially reduces to eq(\ref{eqn:simplified-modified-wave-eqn}) found before when the background metric $F_{\mu \nu} = 2 G_{\mu \nu}$ is fixed i.e $\partial _{\lambda} F_{\mu \nu} = 0$.
